Preliminary Draft

### 2021-07-15 article/draft.tex
correct a bit the section about Facebook flags

No information regarding the flags can be found on Buzzsumo or CrowdTangle, the two APIs we use to access Facebook data. To verify Facebook’s flag policy, only two options are possible: manually or by scraping Facebook.

To better understand the banners implemented by Facebook, we searched for all the Facebook posts having shared a link rated as ‘False’ by Science Feedback with the `search` endpoint in minet. \footnote{ link: \href{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html}{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html}{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html} and its fact-check: \href{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}). The command can be found here: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_crowdtangle\_false\_link.sh}{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_crowdtangle\_false\_link.sh}.} We collected 20 Facebook posts and we manually opened them to verify whether they were flagged with an information banner, a fact-check flag, both or none (2 posts were unavailable so only 18 were categorized). As Science Feedback has sent a False fact-check for this link to Facebook, we would expect all these posts to contain a fact-check flag, but we had no expectations for the information banner.

\begin{figure}
\centering
\includegraphics[scale=0.35]{./img/fb_flags/fb_flag_1.png}
\includegraphics[scale=0.35]{./img/fb_flags/fb_flag_2.png}
\includegraphics[scale=0.45]{./img/fb_flags/fb_flag_3.png}
\caption{Examples of the Facebook posts having shared a link fact-checked False by one of Facebook’s partners (Screenshots taken on July 8, 2021: \href{https://www.facebook.com/groups/1220117708132394/permalink/2386760061468147}{https://www.facebook.com/groups/1220117708132394/permalink/2386760061468147},  \href{https://www.facebook.com/groups/473809623000471/permalink/1333200093728082}{https://www.facebook.com/groups/473809623000471/permalink/1333200093728082}, \href{https://www.facebook.com/691911990845585/posts/3835629366473816}).} 
\label{fb_flags}
\end{figure}

We observed that 11 posts out of 18 had a ‘False information’ flag. We observed that the posts with the ‘False information’ flag were also the ones with a preview of the link (i.e. the banner with an image of the link that we can click on). As the ‘False information’ flag is applied on the preview of the link, and not on the link itself, a user could share a link without the ‘False information’ banner as in the first example of Figure  \ref{fb_flags}.

We also observed that most of the posts (14 out of 18) had an information banner saying ‘Visit the COVID-19 Information Centre for vaccine resources’ (see the first two examples of Figure \ref{fb_flags}). We could not identify why the banner was applied on some posts and not on others (we saw no clear difference in the post message for example).

\begin{table}[]
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{4}{|c|}{Number of posts}                                                                                                                    \\ \hline
with no flag & with an information flag & with a fact-check flag & \begin{tabular}[c]{@{}c@{}}with a fact-check \\ and an information flags\end{tabular} \\ \hline
0            & 7                        & 4                      & 7                                                                                     \\ \hline
\end{tabular}
%\caption{Count for the Facebook posts with the different types of flags having shared a link fact-checked False by one of Facebook’s partners}
%\label{tab_flags}
\end{table}

>>>>

No information regarding the flags can be found on Buzzsumo or CrowdTangle, the two APIs we use to access Facebook data. The only way to verify Facebook’s flag policy is thus to scrap Facebook. For this paper, we added a new feature in minet to scrape Facebook posts and automatically verify for the presence of the flags.

We first searched for all the Facebook posts having shared a link rated as ‘False’ by Science Feedback with the `search` endpoint in minet\footnote{ link: \href{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html}{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html} and its fact-check: \href{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}).}. 20 Facebook posts were collected this way, and the newly developed scraper was used to verify whether they were flagged with an information banner, a fact-check flag, both or none. 3 posts were unavailable, and thus could not be categorized by the scraper. As Science Feedback has sent a False fact-check for this link to Facebook, we would expect all these posts to contain a fact-check flag, but we had no expectations for the information banner.

\begin{figure}
\centering
\includegraphics[scale=0.35]{./img/fb_flags/fb_flag_1.png}
\includegraphics[scale=0.35]{./img/fb_flags/fb_flag_2.png}
\includegraphics[scale=0.45]{./img/fb_flags/fb_flag_3.png}
\caption{Examples of the Facebook posts having shared a link fact-checked False by one of Facebook’s partners (Screenshots taken on July 8, 2021: \href{https://www.facebook.com/groups/1220117708132394/permalink/2386760061468147}{https://www.facebook.com/groups/1220117708132394/permalink/2386760061468147},  \href{https://www.facebook.com/groups/473809623000471/permalink/1333200093728082}{https://www.facebook.com/groups/473809623000471/permalink/1333200093728082}, \href{https://www.facebook.com/691911990845585/posts/3835629366473816}{https://www.facebook.com/691911990845585/posts/3835629366473816}).} 
\label{fb_flags}
\end{figure}

Surprinsingly only 11 posts out of the remaining 17 had a ‘False information’ flag  (see Table \ref{tab_flags_fb}). We observed that the flagged posts were also the ones in which the false link was expanded (i.e., a banner was visible with an image of the link and that can be clicked on, see the middle and right panels of Figure \ref{fb_flags} for examples). As the ‘False information’ flag is applied on the link banner, and not on the link itself, a user could share a link without the ‘False information’ banner as in the first example of Figure \ref{fb_flags}.

We also observed that most of the posts (13 out of 17, see Table \ref{tab_flags_fb}) had an information banner saying ‘Visit the COVID-19 Information Centre for vaccine resources’ (see the first two examples of Figure \ref{fb_flags}). We could not identify why the banner was applied on some posts and not on others (we saw no clear difference in the post messages for example). It should be noted that some posts displayed both the information and the fact-check banners, as in the right panel of Figure \ref{fb_flags}.

\begin{table}[]
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{4}{|c|}{Number of posts}                                                                                                                    \\ \hline
with no flag & with an information flag & with a fact-check flag & \begin{tabular}[c]{@{}c@{}}with a fact-check \\ and an information flags\end{tabular} \\ \hline
0            & 7                        & 4                      & 7                                                                                     \\ \hline
\end{tabular}
\caption{Count for the Facebook posts with the different types of flags having shared a link fact-checked False by one of Facebook’s partners}
\label{tab_flags_fb}
\end{table}
